\disstitle

### 2018-06-16 chapters/introduction/introduction.tex
updates

It is not a trivial task for machines to understand images in general.
To achieve this goal, researchers adopt a divide-and-conquer strategy,
that is divide image understanding into various sub-problems like
object recognition, semantic segmentation, and pose estimation \etc.
During the past decades, a lot of methods are developed to solve there
sub-problem, many of them adopted a bottom-up (\todo{citations})
workflow, where basic level cues play important roles
(\todo{examples}). Among there basic cues, camera geometry are
particularly useful for some computer vision tasks like facade
detection, indoor layout estimation~\cite{ren2016coarse}.

@@

During past dacades, many research has been done to detect the camera
geometry from input images. \todo{citation and examples}. Most of the
previous work optimize for a limited set of camera calibration
parameters only. However, our research found that there exists an
effective way of optimizing multiple camera calibration parameters at
simultaneously (refer to \chapref{mcmc}). Our method use the Monte
Carlo Markov Chain (MCMC) method to sample the possible solutions that
minimize the objective function, which measure the ``matchness''
between the observation (input image) and the camera calibration.

Among the most influential approaches for camera geometry estimation,
most methods are based on traditional statistics diagram. Not until a
fewer years ago, machine learning based methods gradually caught
people's attention in this area, thanks for the popularity of deep
neural network. Neural networks were first proposed in 80th
(\todo{citation}), The back-forward method develop by Hinton
\todo{citation} makes the effective training possible. However neural
networks are generally thought by researchers merely toy that can only
solve a very limited set of tasks. It is the develop of computational
resources and the big collection of annotated data that make the
neural networks deeper and eventually bring it to the stage of
industrial applications.

@@

In our work, we have shown that deep neural networks are powerful
tools for camera geometry estimation. In fact, the camera
geometry can also assist learning high-level image semantics.
Hoiem \etal~\cite{hoiem2008putting} demonstrate that taking camera
perspective (horizon line) into consideration improves the performance
for object detection. Godard \etal~\cite{godard2017unsupervised}
learn to predict the scene depth from a single image using left-right
consistency, which is also an application of camera geometry.
\todo{more citations about the projective loss}.

Another example of camera geometry boosting the learning project is to
exploit the overhead imagery. Using the geometric locations of the
ground-view images we can download the corresponding overhead images
at the same locations through public online resources like bingmap
\todo{cite}.
%
\todo{copy from scott} More recently, efforts have been made to
automate overhead image analysis. As early as
1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.
\brief{overhead image grows fast}.

\todo{expand this paragraph}
Camera geometry can also be used as weak annotations during training
of the networks for image understanding.

\section{Our Approach}
My thesis focuses on the image understanding with camera geometry.
There are two directions we will address: 1) How can we obtain camera
geometry from images; 2) How can we use camera geometry to improve the
current methods for image semantic extracting. For the first direction,
we explore both the traditional method and deep learning approaches on
different geometric calibration parameters. For the second direction,
we will exploit the image geometric location to help extract
semantically meaningful informations from images.

>>>>

It is not a trivial task for machines to understand images in general.
To achieve this goal, researchers adopt a divide-and-conquer strategy,
that is dividing image understanding into various sub-problems like
object recognition, semantic segmentation, and pose estimation \etc.
During past decades, a lot of methods are developed to solve
these
sub-problems. Many of them adopted a bottom-up (\todo{citations})
workflow, where basic level cues play important roles
(\todo{examples}). Among these basic cues, camera geometry is
particularly useful for some computer vision tasks like facade
detection, indoor layout estimation~\cite{ren2016coarse}.

@@

Many research has been done to detect the camera
geometry from input images. \todo{citation and examples}. Most of the
previous work optimize for a limited set of camera calibration
parameters only. However, our research found that there exists an
effective way of optimizing multiple camera calibration parameters at
simultaneously (refer to \chapref{mcmc}). Our method use the Monte
Carlo Markov Chain (MCMC) method to sample the possible solutions that
minimize the objective function, which measures the ``matchness''
between the observation (input image) and the camera calibration.

Among the most influential approaches for camera geometry estimation,
most methods are based on traditional statistics diagram. Not until a
fewer years ago, machine learning based methods gradually caught
people's attention in this area, thanks for the popularity of deep
neural network. Neural networks were first proposed in 80th
(\todo{citation}), The back-forward method developed by Hinton
\todo{citation} makes the effective training possible. However, neural
networks are generally thought by researchers merely toy that can only
solve a very limited set of tasks. It is the develop of computational
resources and the big collection of annotated data that enables the
neural networks to grow deeper and eventually brings it to the stage of
industrial applications.

@@

In our previous work, we have shown that deep neural networks are
powerful tools for camera geometry estimation as well. In fact, the
camera geometry can also assist learning high-level image semantics.
Hoiem \etal~\cite{hoiem2008putting} demonstrate that taking camera
perspective (horizon line) into consideration improves the performance
for object detection. Godard \etal~\cite{godard2017unsupervised} learn
to predict the scene depth from a single image using left-right
consistency, which is also an application of camera geometry.
\todo{more citations about the projective loss}.

Another example of camera geometry boosting the learning project is to
exploit the overhead imagery. Using the geometric locations of the
ground-view images we can download the corresponding overhead images
at the same locations through public online resources like bingmap
\todo{cite}. We refer to these image pairs as ``cross-view image
pairs''.

\todo{copy from scott} Efforts have been made to
automate overhead image analysis. As early as
1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.
%\brief{overhead image grows fast}.

Our work demonstrates that we are able to transfer the learned semantic
knowledge from the ground image domain to the overhead image domain,
given the camera geometric information of these two kind of images. In
our algorithm, the camera geometry helps to collect the ``cross-view
image pairs'' and aligned the orientation directions of images in a
pair.

Camera geometry can also be used as weak annotations during training
of the networks for image understanding.  One of the key to the
success of machine learning approaches are the large quantity of
annotated data. However, fully annotated imagery consists of only a
tiny part of the image resources available online. The idea is to
exploit other meta-info that are automatically recorded/captured by
devices to train the ML models. One of the meta-info potentially
helpful for learning is camera geometry.  We demonstrate that the
camera geometry can be used as weak ground truth for supervision
problem. By learning the capture time and the geolocation of the
images simultaneously, our network is able capture the geo-temporal
related high-level features.

\section{Our Approach}
My thesis focuses on the image understanding with camera geometry.
There are two directions we will address: 1) How to estimate camera
geometry from images; 2) How can we use camera geometry to improve the
current methods for image semantic extracting. For the first direction,
we explore both the traditional method and deep learning approaches on
different geometric calibration parameters. For the second direction,
we will exploit the image geometric location to help extract
semantically meaningful informations from images.
